%------------------------------------------------------------------------------
\chapter*{List of abbreviations}
%------------------------------------------------------------------------------
\begin{description}
\item [{API:}] \underline{A}pplication \underline{p}rogramming \underline{i}nterface
\item [{RSA:}] \underline{R}ivest-\underline{S}hamir-\underline{A}dleman: \index{RSA}
               a public-key cryptosystem which is widely used for secure data 
               transmission
\item [{SSH:}] \underline{S}ecure \underline{sh}ell: \index{SSH}
               a cryptographic network protocol for operating network services 
               securely over an unsecured network.
\end{description}
% ---------------------------------------------------------------------------- %

%------------------------------------------------------------------------------
\chapter{Building libGit2 and libSSH2\label{chap:building_git2_ssh2}}
%------------------------------------------------------------------------------
\section{libgit2}
%------------------------------------------------------------------------------

This section includes a description on how the libgit2 library was build and 
uploaded into the project. Under normal circumstances you can simply use this
library, and it is not needed to follow the instructions below. Only in cases
you need a bug fix, a specific new feature or need the library for an additional
operating system, then you may need to go through this process. Please note, 
that things may have changed for a new library.

\begin{itemize}
\item Install CMake (see \S\ref{sec:install_cmake})
\item Create a github account (see \S\ref{sec:Create_a_github_account})
\item First we need libssh2, found it on website: \url{https://github.com/libssh2}
\item Cloned libssh2 from github: \url{https://github.com/libssh2/libssh2}
      using command:\\
      !git clone git@github.com:libssh2/libssh2.git!\\
      (For Windows used !git-bash.bat! which is a mingw64 terminal, and navigated to the !procts! directory)
\item Extend your path with CMake:\\
      !export PATH=$PATH:/c/Program\ Files/CMake/bin!
\item !cd libssh2!
\item !mkdir build32!
\item !cd build32!
\item For windows 32 build:\\
      !cmake -G "Visual Studio 15 2017" ..!
\item For Windows 32 Debug:\\
      !cmake --build . --config Debug!\\
      For Windows 32 Release:\\
      !cmake --build . --config Release!
\item You'll find !libssh2.lib! in the directory !libssh2/Build32/src/Debug! and 
      !libssh2/Build32/src/Release!
\item !cd ..!
\item !mkdir build64!
\item !cd build64!
\item For windows 64 build:\\
      !cmake -G "Visual Studio 15 2017 Win64" ..!
\item For Windows 64 Debug:\\
      !cmake --build . --config Debug!\\
      For Windows 64 Release:\\
      !cmake --build . --config Release!
\item You'll find !libssh2.lib! in the directory !libssh2/Build64/src/Debug! and 
      !libssh2/Build64/src/Release!
\item You'll find include files in the !libssh2/include! directory
\item !cd ../..!
\item Found libgit2 on the website: \url{https://libgit2.github.com/}
\item Cloned libgit2 from github: \url{https://github.com/libgit2/libgit2}
      using command:\\
      !git clone git@github.com:libgit2/libgit2.git!\\
      (For Windows used !git-bash.bat! which is a mingw64 terminal, and navigated to the !procts! directory)
\item !export LIBSSH2_INCLUDE_DIRS=P:/ath/to/procts/libssh2/include!\\
      (Please note the windows notation !P:!. Replace !P:/ath/to! by your path to !procts!)
\item !cd libgit2!
\item !mkdir build32!
\item !cd build32!
\item For windows 32 build:\\
      !cmake -G "Visual Studio 15 2017" -DBUILD_CLAR=OFF -DBUILD_SHARED_LIBS=OFF -DTHREADSAFE=ON ..!
\item For Windows 32 Debug:\\
      !cmake --build . --config Debug!\\
      For Windows 32 Release:\\
      !cmake --build . --config Release!
\item You'll find !git2.lib! in the directory !libgit2/build32/Debug! and 
      !libgit2/build32/Release!
\item For debug, also copy !git2internal.pdb!, !http-parser.pdb!, !regex.pdb! and !zlib.pdb! from
      !...\libgit2\build32\...\Debug! to !.../procts/share000/ext/lib/git2/winx86d!
\item !cd ..!
\item !mkdir build64!
\item !cd build64!
\item For windows 64 build:\\
      !cmake -G "Visual Studio 15 2017 Win64" -DBUILD_CLAR=OFF -DBUILD_SHARED_LIBS=OFF -DTHREADSAFE=ON ..!
\item For Windows 64 Debug:\\
      !cmake --build . --config Debug!\\
      For Windows 64 Release:\\
      !cmake --build . --config Release!
\item You'll find !git2.lib! in the directory !libgit2/build64/Debug! and 
      !libgit2/build64/Release!
\item For debug, also copy !git2internal.pdb!, !http-parser.pdb!, !regex.pdb! and !zlib.pdb! from
      !...\libgit2\build64\...\Debug! to !.../procts/share000/ext/lib/git2/winx64d!
\item You'll find !git2.h! in the !libgit2/include! directory
\end{itemize}
In windows the !git2.lib! depends on !crypt32.lib! (also for 64 bit), 
!rpcrt4.lib! and !winhttp.lib!.
Add these libraries to `Additional dependencies' for `Linker' in the project
where you wish to use !git2.lib!.

%------------------------------------------------------------------------------
\section{Create a github account}\label{sec:Create_a_github_account}
%------------------------------------------------------------------------------

\begin{itemize}
\item T.B.C.
\item Navigate to `Settings' \url{https://github.com/settings}
\item Navigate to `SSH and GPG keys' \url{https://github.com/settings/keys}
\item Press `New SSH key'
\item Paste the key as created in the \S\ref{sec:Create_an_RSA_key}
\end{itemize}

%------------------------------------------------------------------------------
\section{Create an RSA key}\label{sec:Create_an_RSA_key}
%------------------------------------------------------------------------------

An RSA \index{RSA} key is needed for SSH \index{SSH} pubkey authentications. See 
\url{https://en.wikipedia.org/wiki/Secure_Shell} and
\url{https://en.wikipedia.org/wiki/RSA_(cryptosystem)} for background information
about RSA and SSH.

\begin{itemize}
\item Open a terminal and run: !cd ~/.ssh && ssh-keygen!
\item Press enter to use the default name !id_rsa!
\item Press enter twice for no or empty passphrase
\item Copy the key to the clipboard with the following command
\begin{description}
    \item[OS X:] !cat id_rsa.pub | pbcopy!
    \item[Linux:] !cat id_rsa.pub | xclip!
    \item[Windows Cygwin/Git Bash:] !cat id_rsa.pub | clip!
\end{description}
\end{itemize}

%------------------------------------------------------------------------------
\section{Install CMake}\label{sec:install_cmake}
%------------------------------------------------------------------------------

\begin{itemize}
\item Found CMake on the website: \url{https://cmake.org/download/}
\item Used release 3.10.0
\begin{description}
    \item[OS X]
    \item[Linux]
    \item[Windows Cygwin/Git Bash]
    \begin{itemize}
        \item Downloaded !cmake-3.10.0-win64-x64.msi!
        \item Execute !cmake-3.10.0-win64-x64.msi!
        \item `Next', `I accept ...', `Next'
        \item `Do not add CMake to the system PATH for the current user', `Next'
        \item `Next', `Install', `Finish'
    \end{itemize}
\end{description}
\end{itemize}

%------------------------------------------------------------------------------
\section{Building with Visual Studio 15.4}
%------------------------------------------------------------------------------

In the transition from 15.3 to 15.4, Microsoft has moved libraries and header files.
One of the missing libraries is !Gdi32.Lib!.

This can be solved by adding the following environment variables:\\
!_LINK_=/LIBPATH:"C:\Program Files (x86)\Windows Kits\10\Lib\10.0.16299.0\um\x64"!\\
!_CL_=/I"C:\Program Files (x86)\Windows Kits\10\Include\10.0.16299.0\um"!\\
Note that the location may differ on you computer.
